### 2014-07-15 Paper_Markdown.Rmd
Found a bug in the codeing of pollen taxa that excludes western Abies from pollen assemblages, effectively changing the assemblages.  Re-ran the analysis using only eastern sample sites.

Sites from across North America were used to build a modern analogue dataset.  Samples were obtained from the North American Modern Pollen Database east of 100oW.  Pollen taxa were standardized as in Gill et al. (in prep), using a set of 54 taxa, similar to those reported in Whitmore et al. (2005).  We chose to exclude Western North America since pollen taxa such as Tsuga canadensis and Tsuga heterophylla may be morphologically indistinct, but taxa have clearly differentiated distributions, thus it may be possible to find false close-analogues using the entire North American dataset.  While this is not, strictly speaking, a major problem for this analysis, it will raise baseline error rates for models which then cause us to underestimate the change in error as analogue distance is increased.

>>>>

Sites from across North America were used to build a modern analogue dataset.  Samples were obtained from the North American Modern Pollen Database east of 100oW.  Pollen taxa were standardized as in Gill et al. (in prep), using a set of 54 taxa, similar to those reported in Whitmore et al. (2005).  We chose to exclude Western North America since pollen taxa such as *Tsuga canadensis* and *Tsuga heterophylla* may be morphologically indistinct, but their parent plant taxa have clearly differentiated distributions, thus it may be possible to find false close-analogues using the entire North American dataset.  While this is not, strictly speaking, a major problem for this analysis, it will raise baseline error rates for models which then cause us to underestimate the change in error as analogue distance is increased.
